PANCHANGE_analysis

### 2020-09-18 PANCHANGE_analysis.Rmd
deleted all regressions and replaced with short forms due to functions

## Prepan-baseline change

@@

```{r}
model0a.estimates(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
model0a.reg.stats(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
```

@@

```{r}
model0b.estimates(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
model0b.reg.stats(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
```

@@

```{r}
model1a.estimates(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
model1a.reg.stats(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
```

@@

```{r}
model1b.estimates(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
model1b.reg.stats(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
```

@@

```{r}
model0a.explan.estimates(outcome = "gad.diff_score_base_prepan", explan_var = "gad.sum_score_retro", data_set = "dat.prepan")
model0a.explan.reg.stats(outcome = "gad.diff_score_base_prepan", explan_var = "gad.sum_score_retro", data_set = "dat.prepan")
```

### CHANGE SCORES

### GAD
Model 0a: Disorder_hierarchical, Unadjusted
```{r GAD prepan Model 0a}
# Model
gad_prepan_model0a <- lm(
  formula = gad.diff_score_base_prepan ~ 
    Disorder_hierarchical,
  data = dat.prepan)

summary(gad_prepan_model0a)

# Regression statistics
gad_prepan_model0a_reg_stats <- glance(gad_prepan_model0a) %>%
  mutate(
    "n" = format(
      round(nobs,
            digits = 0),
      nsmall = 0),
    "R2" = format(
      round(r.squared,
            digits = 2),
      nsmall = 2),
    "adjust. R2" = format(
      round(adj.r.squared,
            digits = 2),
      nsmall = 2),
    "F" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
  )
  ) %>%
  select(
    "n",
    "R2",
    "adjust. R2",
    "F",
    "p value",
    "df"
  )

kable(gad_prepan_model0a_reg_stats)
gad_prepan_model0a_reg_stats

# Estimate summary table
gad_prepan_model0a_estimates <- tidy(gad_prepan_model0a, conf.int = TRUE) %>%
  mutate(
    "Indepent variable" = recode_factor(
      term,
      "(Intercept)" = "Intercept",
      "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
      "Disorder_hierarchicalEating disorders" = "Eating disorders",
      "Disorder_hierarchicalOCDs" = "OCDs",
      "Disorder_hierarchicalPTSD" = "PTSD",
      "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
      "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders"
    ),
    "Estimate" = format(
      round(estimate,
            digits = 2),
      nsmall = 2),
    "95% CI low" = format(
      round(conf.low,
            digits = 2),
      nsmall = 2),
    "95% CI up" = format(
      round(conf.high,
            digits = 2),
      nsmall = 2),
    "SE" = format(
      round(std.error,
            digits = 2),
      nsmall = 2),
    "z score" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
  )
  ) %>%
  select(
    "Indepent variable",
    "Estimate",
    "95% CI low",
    "95% CI up",
    "SE",
#    "z score",
    "p value"
  )

kable(gad_prepan_model0a_estimates)
gad_prepan_model0a_estimates
```

Model 0b: Overlapping disorders, Unadjusted
```{r GAD prepan Model 0b}
gad_prepan_model0b <- lm(
  formula = gad.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

summary(gad_prepan_model0b)

# Regression statistics
gad_prepan_model0b_reg_stats <- glance(gad_prepan_model0b) %>%
  mutate(
    "n" = format(
      round(nobs,
            digits = 0),
      nsmall = 0),
    "R2" = format(
      round(r.squared,
            digits = 2),
      nsmall = 2),
    "adjust. R2" = format(
      round(adj.r.squared,
            digits = 2),
      nsmall = 2),
    "F" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
  )
  ) %>%
  select(
    "n",
    "R2",
    "adjust. R2",
    "F",
    "p value",
    "df"
  )

kable(gad_prepan_model0b_reg_stats)
gad_prepan_model0b_reg_stats

# Estimate summary table
gad_prepan_model0b_estimates <- tidy(gad_prepan_model0b) %>%
  mutate(
    "Indepent variable" = recode_factor(
      term,
      "(Intercept)" = "Intercept",
      "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
      "depressive_disordersDepressive disorder" = "Depressive disorders",
      "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
      "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
      "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
      "eating_disordersEating disorder" = "Eating disorders",
      "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
      "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
      "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
      "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
      "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
      "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
      "mhd.personality_disorderPersonality disorder" = "Personality disorder"
    ),
    "Estimate" = format(
      round(estimate,
            digits = 2),
      nsmall = 2),
    "SE" = format(
      round(std.error,
            digits = 2),
      nsmall = 2),
    "z score" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
  )
  ) %>%
  select(
    "Indepent variable",
    "Estimate",
    "SE",
#    "z score",
    "p value"
  )

kable(gad_prepan_model0b_estimates)
gad_prepan_model0b_estimates
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD prepan Model 1a}
gad_prepan_model1a <- lm(
  formula = gad.diff_score_base_prepan ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(gad_prepan_model1a)

# Regression statistics
gad_prepan_model1a_reg_stats <- glance(gad_prepan_model1a) %>%
  mutate(
    "n" = format(
      round(nobs,
            digits = 0),
      nsmall = 0),
    "R2" = format(
      round(r.squared,
            digits = 2),
      nsmall = 2),
    "adjust. R2" = format(
      round(adj.r.squared,
            digits = 2),
      nsmall = 2),
    "F" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
    )
  ) %>%
  select(
    "n",
    "R2",
    "adjust. R2",
    "F",
    "p value",
    "df"
  )

kable(gad_prepan_model1a_reg_stats)
gad_prepan_model1a_reg_stats

# Estimate summary table
gad_prepan_model1a_estimates <- tidy(gad_prepan_model1a) %>%
  mutate(
    "Indepent variable" = recode_factor(
      term,
      "(Intercept)" = "Intercept",
      "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
      "Disorder_hierarchicalEating disorders" = "Eating disorders",
      "Disorder_hierarchicalOCDs" = "OCDs",
      "Disorder_hierarchicalPTSD" = "PTSD",
      "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
      "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
      "Gender_collapsedFemale" = "Female",
      "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
      "age_category_collapsed19-25" = "19-25 years",
      "age_category_collapsed26-35" = "26-35 years",
      "age_category_collapsed36-45" = "36-45 years",
      "age_category_collapsed46-55" = "46-55 years",
      "age_category_collapsed56-65" = "56-65 years",
      "age_category_collapsed66-70" = "66-70 years",
      "age_category_collapsed71-75" = "71-75 years",
      "age_category_collapsed76+" = "76+ years",
      "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
      "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
      "Ethnicity_collapsedAfrican or African British" = "African or African British",
      "Ethnicity_collapsedOther" = "Other ethnicity",
      "time_diff_sign_up_coping" = "Time difference: prepandemic to COPING"
    ),
    "Estimate" = format(
      round(estimate,
            digits = 2),
      nsmall = 2),
    "SE" = format(
      round(std.error,
            digits = 2),
      nsmall = 2),
    "z score" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
    )
  ) %>%
  select(
    "Indepent variable",
    "Estimate",
    "SE",
    #    "z score",
    "p value"
  )

kable(gad_prepan_model1a_estimates)
gad_prepan_model1a_estimates
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD prepan Model 1b}
gad_prepan_model1b <- lm(
  formula = gad.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

summary(gad_prepan_model1b)
tidy(gad_prepan_model1b)
```

### PHQ
Model 0a: Disorder_hierarchical, Unadjusted
```{r PHQ prepan Model 0a}
phq_prepan_model0a <- lm(
  formula = phq.diff_score_base_prepan ~ 
    Disorder_hierarchical,
  data = dat.prepan)

summary(phq_prepan_model0a)
tidy(phq_prepan_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r PHQ prepan Model 0b}
phq_prepan_model0b <- lm(
  formula = phq.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

summary(phq_prepan_model0b)
tidy(phq_prepan_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ prepan Model 1a}
phq_prepan_model1a <- lm(
  formula = phq.diff_score_base_prepan ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(phq_prepan_model1a)
tidy(phq_prepan_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ prepan Model 1b}
phq_prepan_model1b <- lm(
  formula = phq.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

summary(phq_prepan_model1b)
tidy(phq_prepan_model1b)
```

### PCL
Model 0a: Disorder_hierarchical, Unadjusted
```{r PCL prepan Model 0a}
pcl_prepan_model0a <- lm(
  formula = pcl.diff_score_base_prepan ~ 
    Disorder_hierarchical,
  data = dat.prepan)

summary(pcl_prepan_model0a)
tidy(pcl_prepan_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r PCL prepan Model 0b}
pcl_prepan_model0b <- lm(
  formula = pcl.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

summary(pcl_prepan_model0b)
tidy(pcl_prepan_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL prepan Model 1a}
pcl_prepan_model1a <- lm(
  formula = pcl.diff_score_base_prepan ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(pcl_prepan_model1a)
tidy(pcl_prepan_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL prepan Model 1b}
pcl_prepan_model1b <- lm(
  formula = pcl.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

summary(pcl_prepan_model1b)
tidy(pcl_prepan_model1b)
```

### OCIR
Model 0a: Disorder_hierarchical, Unadjusted
```{r OCIR prepan Model 0a}
ocir_prepan_model0a <- lm(
  formula = ocir.diff_score_base_prepan ~ 
    Disorder_hierarchical,
  data = dat.prepan)

summary(ocir_prepan_model0a)
tidy(ocir_prepan_model0a)
```

>>>>

# Functions

@@

@@

@@

@@

@@

```{r model0b.explan function}
model0b.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var, 
                             "anxiety_disorders",
                             "depressive_disorders",
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "psychotic_disorders",
                             "mhd.mania_hypomania_bipolar_or_manicdepression",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

  # run the glm
  assign(paste0(outcome,".",explan_var,".model0b.explan"),
         lm( formula = glm.formula,
             data = get(data_set)
         )
  )

  assign(paste0(outcome,".",explan_var,"model0b.explan_estimates"),
         tidy(get(paste0(outcome,".",explan_var,".model0b.explan")), conf.int = TRUE) %>%
           mutate(
             "Indepent variable" = recode_factor(
               term,
               "(Intercept)" = "Intercept",
               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
               "depressive_disordersDepressive disorder" = "Depressive disorders",
               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
               "eating_disordersEating disorder" = "Eating disorders",
               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
               "mhd.personality_disorderPersonality disorder" = "Personality disorder"
             ),
             "Estimate" = format(
               round(estimate,
                     digits = 2),
               nsmall = 2),
             "95% CI low" = format(
               round(conf.low,
                     digits = 2),
               nsmall = 2),
             "95% CI up" = format(
               round(conf.high,
                     digits = 2),
               nsmall = 2),
             "SE" = format(
               round(std.error,
                     digits = 2),
               nsmall = 2),
             "z score" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "Indepent variable",
             "Estimate",
             "95% CI low",
             "95% CI up",
             "SE",
             #    "z score",
             "p value"
           )
  )

  return(get(paste0(outcome,".",explan_var,"model0b.explan_estimates")))
}

model0b.explan.reg.stats <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("Disorder_hierarchical")
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

  # run the glm
  assign(paste0(outcome,".",explan_var,".model0b.explan"),
         lm( formula = glm.formula,
             data = get(data_set)
         )
  )

  assign(paste0(outcome,".",explan_var,"model0b.explan_reg_stats"),
         glance(get(paste0(outcome,".",explan_var,".model0b.explan"))) %>%
           mutate(
             "n" = format(
               round(nobs,
                     digits = 0),
               nsmall = 0),
             "R2" = format(
               round(r.squared,
                     digits = 2),
               nsmall = 2),
             "adjust. R2" = format(
               round(adj.r.squared,
                     digits = 2),
               nsmall = 2),
             "F" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "n",
             "R2",
             "adjust. R2",
             "F",
             "p value",
             "df"
           )
  )

  return(get(paste0(outcome,".",explan_var,"model0b.explan_reg_stats")))
}
```

```{r model1a.explan function}
model1a.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "Disorder_hierarchical",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "time_diff_sign_up_coping"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

  # run the glm
  assign(paste0(outcome,".",explan_var,".model1a.explan"),
         lm( formula = glm.formula,
             data = get(data_set)
         )
  )

  assign(paste0(outcome,".",explan_var,"model1a.explan_estimates"),
         tidy(get(paste0(outcome,".",explan_var,".model1a.explan")), conf.int = TRUE) %>%
           mutate(
             "Indepent variable" = recode_factor(
               term,
               "(Intercept)" = "Intercept",
               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
               "Disorder_hierarchicalEating disorders" = "Eating disorders",
               "Disorder_hierarchicalOCDs" = "OCDs",
               "Disorder_hierarchicalPTSD" = "PTSD",
               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
               "Gender_collapsedFemale" = "Female",
               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
               "age_category_collapsed19-25" = "19-25 years",
               "age_category_collapsed26-35" = "26-35 years",
               "age_category_collapsed36-45" = "36-45 years",
               "age_category_collapsed46-55" = "46-55 years",
               "age_category_collapsed56-65" = "56-65 years",
               "age_category_collapsed66-70" = "66-70 years",
               "age_category_collapsed71-75" = "71-75 years",
               "age_category_collapsed76+" = "76+ years",
               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
               "Ethnicity_collapsedAfrican or African British" = "African or African British",
               "Ethnicity_collapsedOther" = "Other ethnicity",
               "time_diff_sign_up_coping" = "Time difference: prepandemic to COPING"
             ),
             "Estimate" = format(
               round(estimate,
                     digits = 2),
               nsmall = 2),
             "95% CI low" = format(
               round(conf.low,
                     digits = 2),
               nsmall = 2),
             "95% CI up" = format(
               round(conf.high,
                     digits = 2),
               nsmall = 2),
             "SE" = format(
               round(std.error,
                     digits = 2),
               nsmall = 2),
             "z score" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "Indepent variable",
             "Estimate",
             "95% CI low",
             "95% CI up",
             "SE",
             #    "z score",
             "p value"
           )
  )

  return(get(paste0(outcome,".",explan_var,"model1a.explan_estimates")))
}

model1a.explan.reg.stats <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("Disorder_hierarchical")
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

  # run the glm
  assign(paste0(outcome,".",explan_var,".model1a.explan"),
         lm( formula = glm.formula,
             data = get(data_set)
         )
  )

  assign(paste0(outcome,".",explan_var,"model1a.explan_reg_stats"),
         glance(get(paste0(outcome,".",explan_var,".model1a.explan"))) %>%
           mutate(
             "n" = format(
               round(nobs,
                     digits = 0),
               nsmall = 0),
             "R2" = format(
               round(r.squared,
                     digits = 2),
               nsmall = 2),
             "adjust. R2" = format(
               round(adj.r.squared,
                     digits = 2),
               nsmall = 2),
             "F" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "n",
             "R2",
             "adjust. R2",
             "F",
             "p value",
             "df"
           )
  )

  return(get(paste0(outcome,".",explan_var,"model1a.explan_reg_stats")))
}
```

```{r model1b.explan function}
model1b.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "anxiety_disorders",
                             "depressive_disorders",
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "psychotic_disorders",
                             "mhd.mania_hypomania_bipolar_or_manicdepression",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "time_diff_sign_up_coping"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

  # run the glm
  assign(paste0(outcome,".",explan_var,".model1b.explan"),
         lm( formula = glm.formula,
             data = get(data_set)
         )
  )

  assign(paste0(outcome,".",explan_var,"model1b.explan_estimates"),
         tidy(get(paste0(outcome,".",explan_var,".model1b.explan")), conf.int = TRUE) %>%
           mutate(
             "Indepent variable" = recode_factor(
               term,
               "(Intercept)" = "Intercept",
               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
               "depressive_disordersDepressive disorder" = "Depressive disorders",
               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
               "eating_disordersEating disorder" = "Eating disorders",
               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
               "Gender_collapsedFemale" = "Female",
               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
               "age_category_collapsed19-25" = "19-25 years",
               "age_category_collapsed26-35" = "26-35 years",
               "age_category_collapsed36-45" = "36-45 years",
               "age_category_collapsed46-55" = "46-55 years",
               "age_category_collapsed56-65" = "56-65 years",
               "age_category_collapsed66-70" = "66-70 years",
               "age_category_collapsed71-75" = "71-75 years",
               "age_category_collapsed76+" = "76+ years",
               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
               "Ethnicity_collapsedAfrican or African British" = "African or African British",
               "Ethnicity_collapsedOther" = "Other ethnicity",
               "time_diff_sign_up_coping" = "Time difference: prepandemic to COPING"
             ),
             "Estimate" = format(
               round(estimate,
                     digits = 2),
               nsmall = 2),
             "95% CI low" = format(
               round(conf.low,
                     digits = 2),
               nsmall = 2),
             "95% CI up" = format(
               round(conf.high,
                     digits = 2),
               nsmall = 2),
             "SE" = format(
               round(std.error,
                     digits = 2),
               nsmall = 2),
             "z score" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "Indepent variable",
             "Estimate",
             "95% CI low",
             "95% CI up",
             "SE",
             #    "z score",
             "p value"
           )
  )

  return(get(paste0(outcome,".",explan_var,"model1b.explan_estimates")))
}

model1b.explan.reg.stats <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("Disorder_hierarchical")
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

  # run the glm
  assign(paste0(outcome,".",explan_var,".model1b.explan"),
         lm( formula = glm.formula,
             data = get(data_set)
         )
  )

  assign(paste0(outcome,".",explan_var,"model1b.explan_reg_stats"),
         glance(get(paste0(outcome,".",explan_var,".model1b.explan"))) %>%
           mutate(
             "n" = format(
               round(nobs,
                     digits = 0),
               nsmall = 0),
             "R2" = format(
               round(r.squared,
                     digits = 2),
               nsmall = 2),
             "adjust. R2" = format(
               round(adj.r.squared,
                     digits = 2),
               nsmall = 2),
             "F" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "n",
             "R2",
             "adjust. R2",
             "F",
             "p value",
             "df"
           )
  )

  return(get(paste0(outcome,".",explan_var,"model1b.explan_reg_stats")))
}
```

# GAD prepan
## Regression: Change scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r gad model0a diff_score prepan}
# Regression coefficients
gad_prepan_model0a_estimates <- model0a.estimates(outcome = "gad.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(gad_prepan_model0a_estimates)
gad_prepan_model0a_estimates

# Regression diagnostic statistics
gad_prepan_model0a_reg_stats <- model0a.reg.stats(outcome = "gad.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(gad_prepan_model0a_reg_stats)
gad_prepan_model0a_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r gad model0b diff_score prepan}
# Regression coefficients
gad_prepan_model0b_estimates <- model0b.estimates(outcome = "gad.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(gad_prepan_model0b_estimates)
gad_prepan_model0b_estimates

# Regression diagnostic statistics
gad_prepan_model0b_reg_stats <- model0b.reg.stats(outcome = "gad.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(gad_prepan_model0b_reg_stats)
gad_prepan_model0b_reg_stats
```
